---
title: "USstocks"
author: "Vignette Author"
date: "`r Sys.Date()`"
output: pdf_document
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

#### Abstract
- Abstract

## Introduction
- Brief introduction to what's in this package 
- Highlight interesting components/results

## Data
- How to access this data?
- Describe where the data came from
- Describe how we "filtered" out the outliers  

USstocks data frame contains the the following variables, which can be viewed by calling: `names(stocks)`: 

- "id" : unique security identifier (randomly generated?)
- "symbol" : stock exchange ticker
- "v.date" : date of observation
- "price.unadj" : unadjusted price
- "price" : price (adjusted)
- "volume.unadj" : unadjusted volume
- "volume": volume (adjusted)
- "tret" : total returns (how is it defined?)
- "m.sec" : sector to which the stock belongs
- "m.ind" : industry to which the stock belongs
- "name" : company name
- "year" : year 
- "cap.usd" : market capitalization (of the year)
- "top.1500" : boolean indicating whether the stock is part of the top 1500 performing in that year


## Cool things
- Looking at performance of stocks over time
- Comparing different stocks 
- Looking at stocks' stability over time 

- Stock Analysis: time-series, simple-moving averages, moving average cross-over with buffer, resistance bands
- Perhaps running regression?  

- Visuals of the stuff above (ggplot2)
- fanplot?

## Removing Outliers 
```{r, eval = FALSE}


## Summary

## Bibliography 

##Potential Code We Could Use
```{r,eval=FALSE}
#This file contains some of the draft R code for 
#what we might want to potentially include in the vignette (rmd file)

#----------------------------------------------------#

library(lubridate)
library(dplyr)
library(tidyr)
library(ggplot2)

library(USstocks)
data(stocks)

###If we want to look at a specific stock and its performance:

#all of the years
filter(stocks, symbol == "MSFT")

#the year 2002
filter(stocks, symbol == "MSFT", year == 2002)
stocks %% filter(symbol == "MSFT", year == 2002)


###Chaining with the %>% operator from dplyr

stocks %>%
  filter(symbol == "IBM") %>%
  arrange(v.date) %>%
  ggplot() + geom_point(aes(x = v.date, y = price.unadj, shape = "price unadjusted", colour = "price unadjusted")) + geom_point(aes(x = v.date, y = price, shape = "price", colour = "price")) 

##Example of Key Statistics
stocks %>% 
  filter(symbol == "IBM") %>%
  summarize(mean_volume = mean(volume))

stocks %>%  
  filter(symbol == "MSFT") %>%
  summarise_each(funs(mean, median), volume, volume.unadj, price, price.unadj)

###If you only want certain parts of the stock, it is very easy to do 
#with the filter() function in dplyr

stocks  %>% 
  filter(top.1500 == "TRUE", volume > 100000, year == 2000) %>%
  tbl_df

##Visualizing returns
#Notice that there are some far outliers in our dataset

stocks  %>% group_by(v.date)  %>% 
  summarize(sd_ret = sd(tret, na.rm = TRUE))  %>% 
  ggplot(aes(v.date, sd_ret)) + geom_point()

## We can use the following command to examine these outliers
x <- stocks
x <- filter(x, tret <= 40)
x  %>% 
  select(-id) %>% 
  filter(row_number(desc(tret)) < 10) %>% 
  arrange(desc(tret))

#Looking at these outliers
stocks  %>% filter(tret > 50) %>% arrange(id)

##Creating a local variable, and then we can mess around with the local variables by deleting outliers
x <- stocks
x <- filter(x, tret <= 50)
#unwanted <- filter(stocks, tret > 50)
#x <- stocks
#x <- filter(x, ! symbol %in% unwanted$symbol)

##Looking at the new standard deviation plot, we've removed a lot of outliers 
x  %>% group_by(v.date)  %>% 
  summarize(sd_ret = sd(tret, na.rm = TRUE))  %>% 
  ggplot(aes(v.date, sd_ret)) + geom_point()
```
